FATE summary results

### 2019-12-11 paper draft.Rmd
Changed to 0.9 loadings threshold for climate plots

@@

>>>>

prop1 <- apply(loadings.1, 2, f)
prop1
keep <- prop1 > 0.90 # changing to 0.90 threshold!

@@

```{r, echo=F}
# trends
# plot.trend <- data.frame(year=1972:2017, trend=as.vector(rotated$trends_mean),
#                          lo=as.vector(rotated$trends_lower),
#                          hi=as.vector(rotated$trends_upper))
# 
# plot.b <- ggplot(plot.trend, aes(year, trend)) +
#   theme_bw() +
#   geom_line(color=cb[3]) +
#   geom_ribbon(aes(ymin=lo, ymax=hi), fill=cb[3], alpha=0.4) +
#   geom_hline(yintercept = 0) + ylab("Trend value") +
#   theme(axis.title.x = element_blank()) + 
#   ggtitle("b) Trend")
# 
# png("combined GOA climate loading and trend plot.png", 8, 4, units = "in", res=300)
# 
# ggpubr::ggarrange(plot.a, plot.b, ncol=2)
# 
# dev.off()
```
